DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-10-11 paper/appendix.tex
Add picar-mini models and source data
MiniModel
train=evens in range(30,60)
val = odds in range(30,60)
use_normal_category = True
train loss = 0.009152407757937908
val loss = 0.08686625957489014

MiniModel2
train=evens in range(30,60)
val = odds in range(30,60)
use_normal_category = False
train loss = 0.018782231956720352
val loss = 0.013224977999925613

In the second method, we use the same data and parameters as  above 
except that now images are labeled as 'curved' and 'straight' and we pick an
equal number of images from each category at each training step to
update the model. In other words, we try to remove bias in selecting
images. We find that the car performed better in practice by applying
this approach as the car displayed a greater ability to stay in the
center of the track (on the white tape).
However, we find that there is a huge discrepency between the training
loss and the validation loss as the former was 0.09, while the latter
was 0.00869---a 10X difference---indicating that the model suffers from
the overfitting problem.

>>>>

In the second method, we use the same data and parameters as  above 
except that now images are labeled as 'curved' and 'straight' and we pick an
equal number of images from each category at each training step to
update the model. In other words, we try to remove bias in selecting
images. We find that the car performed better in practice by applying
this approach as the car displayed a greater ability to stay in the
center of the track (on the white tape).
However, we find that there is a huge discrepency between the training
loss and the validation loss as the former was 0.009, while the latter
was 0.0869---a 10X difference---indicating that the model suffers from
the overfitting problem.
